Title

### 2020-08-06 paper.tex
adds more text

\section{General Results}

\begin{itemize}
	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
\end{itemize}

>>>>

	As seen in figure\todo{Insert 3D plot here}, the temperature dependence for the superconducting state is richer than for the normal state described in~\cite{QubitRelax}.
	When $\omega$ and $T$ are both much smaller than $T_c$, the figure reveals the expected reduction in noise.
	As $T \rightarrow T_c$, a smaller $\omega$ is required to facilitate Johnson noise.
	In figure\todo{Insert chi vs T plot, for Lindhard and Nam}, the more sensitive temperature dependence of the superconductor is visible against a normal state calculation done with the Lindhard function, as in~\cite{QubitRelax}.
	For $T \rightarrow T_c$, the superconducting state noise approaches that of the normal state, as expected.
